Laplacian envelope

### 2015-06-01 Notes/laplace.tex
comment
envelope section

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{ideal}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Laplacian envelope}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

@@

The constraints on $\Mh\potdep$ are less stringent than the constraints on $\M\potdep$, \eqref{eq:constr}.
Clearly
%
\begin{equation}\label{eq:constrhoffdiag}
  \Mh\potdep_{i \neq j} \geq 0, \qquad
  \sum_j \Mh\potdep_{ij} = 1.
\end{equation}
%
The ``off-diagonal'' constraints are more complicated.
There can be many $\M\potdep,\hom$ that result in the same $\Mh\potdep$.
However, the fact that $\M\potdep_{ij} \in [0,1]$ and $\hom_{i\neq j} \geq 0$ imply that $\forall (i \neq j)$:
%
\begin{equation}\label{eq:homrange}
  2r\max\brc{f\pot(\Mh\pot_{ij}-1),f\dep(\Mh\dep_{ij}-1)} \leq \hom_{ij} \leq 2r\min\brc{f\pot\Mh\pot_{ij},f\dep\Mh\dep_{ij}}
\end{equation}
%
These two bounds are consistent when
%
\begin{equation}\label{eq:homconsistent}
  -f\dep \leq f\pot\Mh\pot_{ij} - f\dep\Mh\dep_{ij} \leq f\pot
  \qquad \forall i\neq j.
\end{equation}
%
To ensure that $\M\potdep_{ii} \geq 0$, we also need to ensure that $\sum_{j\neq i}\M\potdep_{ij} \leq 1$.
%
\begin{equation}\label{eq:homdiag}
\begin{aligned}
  \sum_{j\neq i} \M\pot_{ij} 
    &= \sum_{j\neq i} \prn{ \Mh\pot_{ij} - \frac{\hom_{ij}}{2rf\pot} }\\
    &\geq \sum_{j\neq i} \prn{ \Mh\pot_{ij} - \frac{1}{f\pot}  \min\brc{ f\pot\Mh\pot_{ij},f\dep\Mh\dep_{ij} } }\\
    &= \frac{1}{f\pot} \sum_{j\neq i} \brk{ f\pot\Mh\pot_{ij}-f\dep\Mh\dep_{ij} }_+ , \\
  \sum _{j\neq i} \M\dep_{ij} 
    &= \frac{1}{f\dep} \sum_{j\neq i} \brk{ f\dep\Mh\dep_{ij}-f\pot\Mh\pot_{ij} }_+ ,
\end{aligned}
\end{equation}
%
where rectification function is $[x]_\pm = x \Theta(\pm x)$, in terms of the Heaviside step function.
Demanding that these quantities are at most 1 is sufficient to ensure that \eqref{eq:homconsistent} is satisfied.

Therefore we find the set of constraints
%
\begin{equation}\label{eq:constrh}
\begin{aligned}
  \Mh\potdep_{i \neq j} &\geq 0, &\qquad
  \sum_{j\neq i} \brk{ f\pot\Mh\pot_{ij}-f\dep\Mh\dep_{ij} }_+ &\leq f\pot, \\
  \sum_j \Mh\potdep_{ij} &=1, &
  \sum_{j\neq i} \brk{ f\dep\Mh\dep_{ij}-f\pot\Mh\pot_{ij} }_+  &\leq f\dep.
\end{aligned}
\end{equation}
%
We showed that these are necessary conditions for the existence of $\M\potdep,\hom$ satisfying \eqref{eq:constr}.
We can see that they are sufficient by choosing $\hom_{ij} = 2r\min\brc{f\pot\Mh\pot_{ij},f\dep\Mh\dep_{ij}}$ for $i \neq j$ and $\hom_{ii}=-\sum_{j \neq i} \hom_{ij}$.

We can then treat the off-diagonal elements of $\Mh\potdep$ as the independent degrees of freedom, subject to these constraints, when maximising the SNR.

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{ideal}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Laplacian envelope}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

If we treat the off diagonal elements as the independent degrees of freedom, with the off diagonal elements determined by the row sum constraints (second column of \eqref{eq:constr}), the constraints are
%
\begin{equation}\label{eq:constri}
  \M\potdep_{i \neq j} \geq 0, \qquad
  \sum_{j\neq i} \M\potdep_{ij} \leq 1, \qquad
  \hom_{i \neq j} \geq 0.
\end{equation}
%
The second of these will be referred to as the ``diagonal'' constraint.

@@

This formula takes the same form as the one in our NIPS paper \cite{Lahiri2013synapse}, where the process $\hom$ was not included.
However, the process $\hom$ still has an impact due to the constraints.

The constraints on $\Mh\potdep$ are less stringent than the constraints on $\M\potdep$, \eqref{eq:constr}.
Clearly
%
\begin{equation}\label{eq:constrhoffdiag}
  \Mh\potdep_{i \neq j} \geq 0, \qquad
  \sum_j \Mh\potdep_{ij} = 1.
\end{equation}
%
The ``diagonal'' constraints are more complicated.
There can be many $\M\potdep,\hom$ that result in the same $\Mh\potdep$.
However, the fact that $\M\potdep_{ij} \in [0,1]$ and $\hom_{i\neq j} \geq 0$ imply that $\forall (i \neq j)$:
%
\begin{equation}\label{eq:homrange}
  2r\max\brc{f\pot(\Mh\pot_{ij}-1),f\dep(\Mh\dep_{ij}-1)} \leq \hom_{ij} \leq 2r\min\brc{f\pot\Mh\pot_{ij},f\dep\Mh\dep_{ij}}
\end{equation}
%
These two bounds are consistent when
%
\begin{equation}\label{eq:homconsistent}
  -f\dep \leq f\pot\Mh\pot_{ij} - f\dep\Mh\dep_{ij} \leq f\pot
  \qquad \forall i\neq j.
\end{equation}
%
To ensure that $\M\potdep_{ii} \geq 0$, we also need to ensure that $\sum_{j\neq i}\M\potdep_{ij} \leq 1$.
%
\begin{equation}\label{eq:homdiag}
\begin{aligned}
  \sum_{j\neq i} \M\pot_{ij}
    &= \sum_{j\neq i} \prn{ \Mh\pot_{ij} - \frac{\hom_{ij}}{2rf\pot} }\\
    &\geq \sum_{j\neq i} \prn{ \Mh\pot_{ij} - \frac{1}{f\pot}  \min\brc{ f\pot\Mh\pot_{ij},f\dep\Mh\dep_{ij} } }\\
    &= \frac{1}{f\pot} \sum_{j\neq i} \brk{ f\pot\Mh\pot_{ij}-f\dep\Mh\dep_{ij} }_+ , \\
  \sum _{j\neq i} \M\dep_{ij}
    &= \frac{1}{f\dep} \sum_{j\neq i} \brk{ f\dep\Mh\dep_{ij}-f\pot\Mh\pot_{ij} }_+ ,
\end{aligned}
\end{equation}
%
where rectification function is $[x]_\pm = x \Theta(\pm x)$, in terms of the Heaviside step function.
Demanding that these quantities are at most 1 is sufficient to ensure that \eqref{eq:homconsistent} is satisfied.

Therefore we find the set of constraints
%
\begin{equation}\label{eq:constrh}
\begin{aligned}
  \Mh\potdep_{i \neq j} &\geq 0, &\qquad
  \sum_{j\neq i} \brk{ f\pot\Mh\pot_{ij}-f\dep\Mh\dep_{ij} }_+ &\leq f\pot, \\
  \sum_j \Mh\potdep_{ij} &=1, &
  \sum_{j\neq i} \brk{ f\dep\Mh\dep_{ij}-f\pot\Mh\pot_{ij} }_+  &\leq f\dep.
\end{aligned}
\end{equation}
%
The second column of this will be referred to as the ``diagonal'' constraints.

We showed that these are necessary conditions for the existence of $\M\potdep,\hom$ satisfying \eqref{eq:constr}.
We can see that they are sufficient by choosing $\hom_{ij} = 2r\min\brc{f\pot\Mh\pot_{ij},f\dep\Mh\dep_{ij}}$ for $i \neq j$ and $\hom_{ii}=-\sum_{j \neq i} \hom_{ij}$.

We can then treat the off-diagonal elements of $\Mh\potdep$ as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\Mh\pot_{ij}}{\Mh\pot_{mn}{}} = \pdiff{\Mh\dep_{ij}}{\Mh\dep_{mn}{}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\Mh\pot_{ij}}{\Mh\dep_{mn}{}} = \pdiff{\Mh\dep_{ij}}{\Mh\pot_{mn}{}} = 0.
\end{equation}
%
It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgh_{ij}{}} = \frac{1}{2f\pot} \pdiff{}{\Mh\pot_{ij}{}} + \frac{1}{2f\dep} \pdiff{}{\Mh\dep_{ij}{}},
  \qquad
  \pdiff{}{\ench_{ij}{}} = \frac{1}{2f\pot} \pdiff{}{\Mh\pot_{ij}{}} - \frac{1}{2f\dep} \pdiff{}{\Mh\dep_{ij}{}},
\end{equation}
%
these satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgh_{ij}}{\frgh_{mn}{}} = \pdiff{\ench_{ij}}{\ench_{mn}{}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgh_{ij}}{\ench_{mn}{}} = \pdiff{\ench_{ij}}{\frgh_{mn}{}} = 0.
\end{equation}
%

\section{Laplace transform}\label{sec:laplace}

\subsection{Fundamental matrix \etc}\label{sec:lfund}

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s\I +\onev\pib -\MM)\inv,
\end{equation}
%
where $\pib$ is an arbitrary row vector satisfying $\pib\onev = \frac{1}{\tau_0} \neq 0$.
This reduces to the fundamental matrix at $s=0$.
We can see that $\onev$ is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau_0}{1+s\tau_0}\onev.
\end{equation}
%
Suppose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\pib$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\pib_k} = (\mathbf{a}\fund(s)\onev) \fund_{ki}(s) 
      = \frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

Then we also define
%
\begin{equation}\label{eq:lfptb}
  \fptb(s) = (\onem\fund\dg(s)-\fund(s))\D,
  \qquad
  \fptb_{ij}(s) = \frac{\fund_{jj}(s)-\fund_{ij}(s)}{\eq_j}.
\end{equation}
%
This reduces to the first passage time matrix at $s=0$, but at other $s$ there is (probably) no relation.

Using the exact same proof as in the case $s=0$, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau}{1+s\tau}$.
We can the define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s)\eq_j \prn{\frac{1\pm\w_j}{2}} =  \sum_{j\in\pm} \fptb_{ij}(s)\eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \eta^w_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w 
    = \eta^+_i(s) - \eta^-_i(s) =2\eta^+_i(s) - \eta(s) =\eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\eta^w_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
These quantities can still be used when $\w$ takes more than two values.

\subsection{Laplace transform of SNR curve}\label{sec:laplaceSNR}

Consider the Laplace transform of the evolution operator:
%
\begin{equation}\label{eq:levol}
  \mathbf{G}(s) = \intd[_0^{\infty}]{t} \e^{(\MM-s) t}.
\end{equation}
%
For $\Re s>0$, we have
%
\begin{equation}\label{eq:levolcalc}
  (s-\MM)\mathbf{G}(s) = \intd[_0^{\infty}]{t} (s-\MM)\e^{(\MM-s) t} = \brk{-\e^{(\MM-s) t}}_0^{\infty} = \I.
\end{equation}
%
As $(s-\MM)$ is invertible for $\Re s>0$, because the real part of all eigenvalues of $\MM$ are nonpositive, we have
%
\begin{equation}\label{eq:levolres}
  \mathbf{G}(s) = (s-\MM)\inv.
\end{equation}
%
For $s=0$, we can avoid problems by replacing $\mathbf{G}(s) \to \fund(s)$.

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurvehom} (ignoring the denominator)
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \sqrt{N} \eq \ench \e^{(r\frgh-s)t} \w \\
   &= \sqrt{N} \eq \ench \prn{s - r\frgh}\inv \w.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\ench\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = \frac{A(s)}{\sqrt{N}} &=  \eq \ench \fund(s) \w \\
    &= \sum_{ijk} \eq_i \ench_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \ench_{ij} (\eta^w_{i}(s) - \eta^w_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

In analogy with the case $s=0$, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    c_k(s) &= \sum_{ij} \eq_i \ench_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \\
    a_i(s) &= \sum_j \eq_i \ench_{ij} (\eta^w_{i}(s) - \eta^w_{j}(s)),\\
    \implies
    \hat{A}(s) &= \sum_k c_k(s) \eq_k \w_k
      = \sum_i a_i(s).
  \end{aligned}
\end{equation}
%

\subsection{Derivatives}\label{sec:lderiv}

Using the same approach as the area bound in \cite{Lahiri2013synapse}, we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
\begin{aligned}
  \pdiff{\hat{A}(s)}{\Mh\potdep_{mn}{}}
     =&\, rf\potdep \eq_m \brk{ \sum_i (\fptb_{mi}(0)-\fptb_{ni}(0)) a_i(s)
     +c_m(s) (\eta^w_m(s) - \eta^w_n(s)) } \\
     &\pm f\potdep \eq_m (\eta^w_m(s) - \eta^w_n(s)).
\end{aligned}
\end{equation}
%

\section{Upper bounds}\label{sec:upperbnds}

\subsection{Area bound}\label{sec:area}

%
\begin{equation}\label{eq:areadef}
  \int[_0^\infty]{dt} \snr(t) = \lim_{\tau\to\infty} \tau \snrb(\tau) = A(0).
\end{equation}
%

The only effect of $\hom$ is in the diagonal constraints (second column of \eqref{eq:constrh} vs.\ second inequality in \eqref{eq:constri}).
However, the area is invariant under the scaling mode:
%
\begin{equation}\label{eq:scale}
  \Mh\potdep - \I \to \lambda (\Mh\potdep - \I).
\end{equation}
%
This means we can always take a set of matrices that violate either version of the diagonal constraints and use \eqref{eq:scale} to create a set of matrices that satisfy them without changing the area.
Therefore, including $\hom$ has no effect on the area bound and the result from \cite{Lahiri2013synapse} applies here as well.

This means that 
%
\begin{equation}\label{eq:areabnd}
  A(0) \leq \frac{\sqrt{N}(M-1)}{r}.
\end{equation}
%
The model that saturates this bound is one of serial topology with $\eq$ concentrated symmtrically at the two end states.

\subsection{Initial SNR}\label{sec:initial}

%
\begin{equation}\label{eq:initdef}
  \snr(0) = \snrb(0) = \lim_{s\to\infty} sA(s).
\end{equation}
%

%
\begin{equation}\label{eq:initbnd}
  \snr(0) \leq \sqrt{N},
\end{equation}
%
at least when $f\pot=f\dep=\frac{1}{2}$.

\subsection{Envelope}\label{sec:envelope}

Now we introduce an eigenvector decomposition for $-\frgh$:
%
\begin{equation}\label{eq:eigendecomp}
  \frgh = - \sum_a q_a \evr^a \evl^a,
  \quad
  \evl^a \evr^b = \delta_{ab},
  \quad
  \frgh \evr^a = -q_a \evr^a,
  \quad
  \evl^a \frgh = -q_a \evl^a.
\end{equation}
%
Then we can write
%
\begin{equation}\label{eqsnreig}
  \snr(t) = \sqrt{N}\sum_a \CI_a \e^{-rt/\tau_a},
  \qquad
  \snrb(\tau) = \sqrt{N}\sum_a \frac{\CI_a}{1+r\tau/\tau_a},
\end{equation}
%
where
%
\begin{equation}\label{eq:snrcoeffs}
  \CI_a = (\eq \ench \evr^a) (\evl^a \w),
  \qquad
  \tau_a = \frac{1}{q_a}.
\end{equation}
%
From \eqref{eq:areabnd} and \eqref{eq:initbnd}, we see that they are subject to the constraints
%
\begin{equation}\label{eq:coeffconstr}
  \sum_a \CI_a \tau_a \leq M-1,
  \qquad
  \sum_a \CI_a \leq 1.
\end{equation}
%
No doubt there are many other constraints that these quantities must satisfy, but we can see what these ones imply for the $\snrb(\tau)$ by maximising it subject to these constraints.

Consider the Lagrangian
%
\begin{equation}\label{eq:envlagrangian}
  \CL = \sum_a \frac{\CI_a}{1+r\tau/\tau_a} + \mu_\CI \prn{1 - \sum_a \CI_a} + \mu_\CA \prn{(M-1) - \sum_a \CI_a \tau_a}.
\end{equation}
%
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:envKTcond}
  \pdiff{\CL}{\CI_a} = 0, \qquad
  \pdiff{\CL}{\tau_a} = 0, \qquad
  \mu_\alpha \geq 0, \qquad
  \pdiff{\CL}{\mu_\alpha} \geq 0, \qquad
  \mu_\alpha\pdiff{\CL}{\mu_\alpha} = 0. 
\end{equation}
%
These are solved by
%
\begin{equation}\label{eq:envsol}
\begin{gathered}
  \CI_1 = 1, \qquad
  \CI_{a>1} = 0, \qquad
  \tau_1 = M-1, \\
  \mu_\CI = \frac{(M-1)^2}{(r\tau + (M-1))^2}, \qquad
  \mu_\CA = \frac{r\tau}{(r\tau+(M-1))^2}. \qquad
\end{gathered}
\end{equation}
%
This leads to the envelope
%
\begin{equation}\label{eq:env}
  \snrb(\tau) \leq \frac{\sqrt{N}(M-1)}{r\tau + (M-1)}.
\end{equation}
%
This is the envelope (``memory frontier'') that we can prove.
Finding more constraints would lower it.
Clearly there have to be more constraints, as \eqref{eq:envsol} indicates that this would be achieved by the same model at all times.
This model would have to saturate both the initial SNR bound \eqref{eq:initbnd} and the area bound \eqref{eq:areabnd}, whereas we saw that they were achieved by different models, which perform well at short/long timescales respectively.
